---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MortgageHelpers

<!-- badges: start -->
<!-- badges: end -->

The goal of MortgageHelpers is to provide functions to calculate aspects of a 
mortgage including monthly payments, total terms and interest

## Installation

You can install the development version of MortgageHelpers from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cuisquare/MortgageHelpers")
```

## Example

You can get the monthly payments for a mortgage as follows:

```{r example}
library(MortgageHelpers)
monthly_payment(rate = 0.015,
                capital = 360000,
                term_months = 30*12
                )
```
You can also go for the whole mortgage details.

```{r wholelifemortgage}
mortgage_first5years <- mortgage_state_allmonths(
  rate = 0.015,
  capital = 360000,
  term_months = 30*12,
  month_num = 30*12)
```


You can then plot the various variables. 

```{r wholelifemortgagecapitalplot}

plot(x = mortgage_first5years$month,
     y = mortgage_first5years$capital,
     xlab = "month",
     ylab = "capital",
     main = "capital during mortgage")

```

```{r wholelifemortgageinterestplot}

plot(x = mortgage_first5years$month,
     y = mortgage_first5years$interest_paid,
     xlab = "month",
     ylab = "monthly interest",
     main = "monthly interest during mortgage")

```
